SiO Molecular Jets around young stars - A numerical perspective

### 2013-07-08 PAPER/ms_final_bv.tex
first rough figs from paper runs added

\section{Results}
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10 and $\beta$ = 10.}
\label{grid}
\end{figure*}
\begin{table*}
\centering
\caption{Summary from parameter runs}
\begin{tabular}{l | l | l | l | l | l }
\hline
Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
Shock \\
\hline\hline
adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
pow1010 & Power law & 10 & 10 &&\\
atm1010 & Atomic & 10 & 10 &&\\
atm101 & Atomic & 10 & 1 &&\\
atm210 & Atomic & 2 & 10 &&\\
tab1010 & Tabulated & 10 & 10 &&\\
tab210 & Tabulated & 2 & 10&&\\
mol1010 & Molecular & 10 & 10&&\\
mol510 & Molecular & 5 & 10&&\\
\hline
\end{tabular}
\label{tab:result1}
\end{table*}

>>>>

\section{Results}
\begin{figure*}
 \includegraphics[width=2.\columnwidth]{\figpath/jetplt1_1010.png}
 \caption{Jet Volume Density for different cooling modes with
   $\eta$ = 10 and $\beta$ = 10.}
\label{grid}
\end{figure*}
\begin{table*}
\centering
\caption{Summary from parameter runs}
\begin{tabular}{l | l | l | l | l | l }
\hline
Run & Cooling Mode & $\eta$ & $\beta$ & Peak Intensity [K] & FWHM at Bow
Shock \\
\hline\hline
adi1010 & Nil (Adiabatic) & 10 & 10 &&\\
pow1010 & Power law & 10 & 10 &&\\
atm1010 & Atomic & 10 & 10 &&\\
atm101 & Atomic & 10 & 1 &&\\
atm210 & Atomic & 2 & 10 &&\\
tab1010 & Tabulated & 10 & 10 &&\\
tab210 & Tabulated & 2 & 10&&\\
mol1010 & Molecular & 10 & 10&&\\
mol510 & Molecular & 5 & 10&&\\
\hline
\end{tabular}
\label{tab:result1}

\end{table*}

\begin{figure}
 \includegraphics[width=84mm]{\figpath/J2-1_mom0maps_cooling.png}
 \caption{A plot of the integrated SiO J2-1 emission from 5 models, each using a different method to calculate cooling and all with $\eta$=10 $\beta$=10.}
\label{cooling2-1}
\end{figure}

\begin{figure*}
 \includegraphics[width=168mm]{\figpath/tabulated_mom0maps_Trans.png}
 \caption{The integrated intensity of 4 SiO transitions in the tabulated cooling model in the $\eta$=2 $\beta$=10 model.}
\label{tabulatedTrans}
\end{figure*}

\begin{figure}
 \includegraphics[width=84mm]{\figpath/tab_trans_spectra.png}
 \caption{The Integrated emission and spectra at he bow shock for 2 transitions of the tabulated cooling model for $\eta$=2 $\beta$=10 (spectra taken from y=50, x=128).}
\label{grid}
\end{figure}
